% main.tex

\section*{Abstract}

\vspace{30pt}

% In this thesis we discuss supersymmetric gauge theories, focusing on exact results achieved using methods of integrability. 
% For the larger part of the work we focus solely on the best known example of an integrable supersymmetric gauge theory, namely the $\N=4$ super Yang-Mills theory.
% After motivating the problem of solving it exactly and briefly reviewing the historical developments in the subject we begin rigorous analysis by firstly defining the theory. 
% We discuss it from the gauge theory point of view and give the alternative string theoretic formulation via the AdS/CFT correspondence.

% We devote a large portion of the thesis for perturbative integrability, which addresses the spectral problem in perturbation theory both in weak and strong coupling. 
% As we develop integrability technology we keep on applying new concepts to the simplest non-trivial observable in the theory, the Konishi operator.
% We find its anomalous dimension using perturbative integrability methods at both ends of the range of the coupling constant.
% At this point we find first hints of exact results by introducing the slope function and exploiting it to extend perturbative results for the Konishi operator.

% Finally we address the most recent developments in solving the spectral problem exactly.
% To that end we introduce the $\pmu$-system after shortly discussing its motivation using the now arguably obsolete TBA and Y-system approaches. 
% We then demonstrate the applicability of this construction by rederiving the slope function and deriving the so called curvature function.
% We show how these exact analytical results can be used to extract further information about the Konishi anomalous dimension. 

% We devote a separate section to the ABJM theory, which is another example of an integrable supersymmetric gauge theory closely related to $\N=4$ supersymmetric Yang-Mills. 
% As most of the techniques in ABJM are analogous to the ones describes while covering $\N=4$ SYM, we only provide a very brief review of results with references to other work containing the details.



In this thesis we discuss supersymmetric gauge theories, focusing on exact results achieved using methods of integrability. 
Historically quantum field theories have always been approached using perturbation theory, which implicitly assumes weak coupling.
However this assumption is not always true, for example the theory describing strong interactions, quantum chromodynamics, is strongly coupled at low energies thus rendering problems like calculating masses of nucleons beyond the reach of perturbation theory.
Supersymmetric theories on the other hand exhibit additional symmetries and structures that when properly exploited can yield new techniques for solving otherwise intractable problems.
The $\N=4$ supersymmetric Yang-Mills theory is a prime example of such a theory, it is known to be integrable which opens up a wealth of techniques one can employ in order to find results valid at any value of the coupling. 

For the larger portion of the text we study the $\N=4$ super Yang-Mills theory, a recurring concept being the Konishi anomalous dimension, which is roughly the analogue for the mass of the proton in quantum chromodynamics.
As expected we begin with perturbation theory where the integrability of the theory first manifests itself.
Here we are able to find the first exact result, the so-called slope function, which is the linear small spin expansion coefficient of the generalized Konishi anomalous dimension.
We then move on to exact results mainly achieved using the novel $\pmu$-system approach, which is a method that allows one to find the scaling dimensions of arbitrary operators at any values of the coupling.
As an example, we are able to find the second coefficient in the small spin expansion after the slope, which we call the curvature function.
This exact result allows us to extract non-trivial information about the Konishi operator.

Methods of integrability are also applicable to other supersymmetric gauge theories, one notable example being ABJM.
It is also known to be integrable and in fact shares many similarities with $\N=4$ super Yang-Mills, which we briefly review.
