% main.tex

\section{Integrability}

In this section we dive into the magical world of integrability.

\subsection{Overview}

Give picture summarizing all techniques and their ranges of applicability.

\subsection{One loop at weak coupling}

Roughly rederive the Minahan/Zarembo result.

\subsubsection{$\mathfrak{su}(2)$ sector}

Give the su(2) Hamiltonian, example states and energies.

\subsubsection{$\mathfrak{sl}(2)$ sector}

Same with sl(2).

\subsection{Higher loops}

Short example of a two loop Hamiltonian, perturbative corrections for the states found above with contact terms.

\subsection{Asymptotic solution}

Generalize su(2) BAE to all loops, maybe give a simple example. 

\subsubsection{A glimpse ahead: the slope function}

Derive slope from ABA.

\subsection{Strong coupling and the algebraic curve construction}

Describe flat connections, monodromies, sheets etc.

\subsection{Classical solutions}

All finite gap solutions can be described this way.

\subsubsection{BMN string}

Give explicit solution.

\subsubsection{Folded string}

Something similar.

\subsection{Quantization and semi-classics}

Describe the quantization procedure. Derive next coefficient for Konishi.

\subsection{Short strings}

Combine with slope, derive next coeffient for Konishi.

\subsection{Full solution to the spectral problem}

Here we finally give the complete solution.

\subsubsection{The full theory}

Mention nested BAE, full psu(2,2|4) spin chain without going into much detail.

\subsubsection{Finite length}

Deprecated approches: TBA, Y-system.

\subsubsection{The $\pmu$ system}

Define $\pmu$ as if it was an axiom.
